Fractional Types

### 2019-11-22 fracGC/p.tex
More on Related work (categorical, quantum lambda)

In addition to the examples presented throughout the paper, we present
examples that provides novel perspectives on gc processes, first as
space transformers, and second as tracing operators. Both ideas are
inspired from known constructions in compact closed
categories~\cite{DBLP:conf/calco/Abramsky05}.

@@

As the diagram below (take from Abramsky's
paper~\cite{DBLP:conf/calco/Abramsky05}) illustrates, this is not a
trivial construction in the sense that the permutation from $A$ to $B$
uses $C$ in non-trivial ways.

@@

There has been ample work on ancillae before us.  For example%
\cite{PhysRevA.94.042337} explicitly represent the lifetime of
quantum wires, enable quantum wires to be recycled, leading
to more efficient circuits.  Interesting applications of
ancillae is in the recent paper~\cite{DBLP:journals/cal/ZhouB19}
on Quantum runtime assertions.  In section~\ref{sub:id}, we
already mentionned dynamic assertion of entanglement; they
also show how to provide (dynamic) assertions on classical
states, and testing of superposition states.  Our techniques
should combine with theirs to provide even more possibilities
for dynamic asserctions. Ancilla management is a complex
business, and the verified circuit compiler
ReVerC~\cite{amy2017verified} goes to great pains to
ensure that ancilla are dealt with properly.  Both
QCL~\cite{omer2002procedural} and Quipper~\cite{Green:2013:QSQ:2491956.2462177}
also do automatic (but not certified) ancilla management during code
generation.  This remains an active area of research, as
outlined in the CACM paper~\cite{valiron2015programming}.

@@

>>>>

In addition to the examples presented throughout the paper, we present
examples that provides novel perspectives on gc processes, first as
space transformers, and second as tracing operators. Both ideas are
inspired from known constructions in compact closed
categories~\cite{dblp:conf/calco/abramsky05}.

@@

As the diagram below (take from Abramsky's
paper~\cite{dblp:conf/calco/abramsky05}) illustrates, this is not a
trivial construction in the sense that the permutation from $A$ to $B$
uses $C$ in non-trivial ways.

@@

There has been ample work on ancillae before us.  For example
\cite{PhysRevA.94.042337} explicitly represent the lifetime of
quantum wires, enable quantum wires to be recycled, leading
to more efficient circuits.  Interesting applications of
ancillae is in the recent paper~\cite{DBLP:journals/cal/ZhouB19}
on Quantum runtime assertions.  In section~\ref{sub:id}, we
already mentionned dynamic assertion of entanglement; they
also show how to provide (dynamic) assertions on classical
states, and testing of superposition states.  Our techniques
should combine with theirs to provide even more possibilities
for dynamic asserctions. Ancilla management is a complex
business, and the verified circuit compiler
ReVerC~\cite{amy2017verified} goes to great pains to
ensure that ancilla are dealt with properly.  Both
QCL~\cite{omer2002procedural} and Quipper~\cite{Green:2013:QSQ:2491956.2462177}
also do automatic (but not certified) ancilla management during code
generation.  This remains an active area of research, as
outlined in the CACM paper~\cite{valiron2015programming}.

@@

Another different thread of work stems from categorical models
of quantum computation, especially those based on dagger
compact closed categories as introduced
in~\cite{Abramsky:2004:CSQ:1018438.1021878}, and greatly
expanded upon in~\cite{abramsky2009categorical}.  Various
results can be obtained in that general setting, such as the
no-cloning theorem~\cite{abramsky2009no}. The $2016$ book
\cite{chiribella2016quantum} is a good survey of the
developments since. Selinger~\cite{selinger2007dagger,Selinger:2011:FDH:1942319.1942398}
has been particularly active in this area. Of particular
note for our applications are two 2005 papers by Abramsky
\cite{abramsky2005structural,dblp:conf/calco/abramsky05}
with explicit examples of circuits using trace that are very useful tests
for our approach.

Also related are various approaches to quantum lambda
calculi, such as~\cite{dblp:journals/mscs/selingerv06,vantonder:2004,dowek2017lineal}.
